Artificial intelligence-assisted analysis of CT abnormalities during COVID-19 recovery

### 2025-03-09 paper/markdown/rebuttal_letter.Rmd

### Issue

Add results in the abstract as well.

### Response

_Anna and Gerlig: I think, we can stress that we were able to model DLCO but not other LFT responses and include some key characteristics of the machine learning models of DLCO < 80% and DLCO. My proposal for the response below._

As suggested, we state now in Abstract, that we were able to establish meaningful models of DLCO and DLCO < 80% but not for other LFT responses. 
We also included key cross-validated performance statistics of meaningful machine learning models at predicting 
DLCO < 80% (accuracy: `r bin_models$stats$DLCO_reduced %>% filter(dataset == 'cv') %>% .$correct_rate %>% range %>% signif(2) %>% paste(collapse = ' - ')`, Cohen's $\kappa$: `r bin_models$stats$DLCO_reduced %>% filter(dataset == 'cv') %>% .$kappa %>% range %>% signif(2) %>% paste(collapse = ' - ')`, AUC: `r bin_models$stats$DLCO_reduced %>% filter(dataset == 'cv') %>% .$AUC %>% range %>% signif(2) %>% paste(collapse = ' - ')`) and 
DLCO expressed as percentage of the patient's reference (mean absolute error [MAE]: `r reg_models$stats$DLCO_percent %>% filter(dataset == 'cv', algorithm != 'nnet') %>% .$MAE %>% range %>% signif(3) %>% paste(collapse = ' - ')`%, $R^2$: `r reg_models$stats$DLCO_percent %>% filter(dataset == 'cv', algorithm != 'nnet') %>% .$rsq %>% range %>% signif(2) %>% paste(collapse = ' - ')`). 
Please note that the later performance statistics of DLCO as % of the patient's reference, we provide the performance metric range for the random forest, GBM, and SVM algorithm, as the neural network model yielded a poor fit (MAE: `r reg_models$stats$DLCO_percent %>% filter(dataset == 'cv', algorithm == 'nnet') %>% .$MAE %>% signif(2)`%, $R^2$: `r reg_models$stats$DLCO_percent %>% filter(dataset == 'cv', algorithm == 'nnet') %>% .$rsq %>% signif(2)`).

@@

### Issue

The literature review part needs to be added.

### Response

_Anna and Gerlig: as above. Below some papersa I found interesting._ 
_https://pubs.rsna.org/doi/full/10.1148/radiol.222888: no modeling but reduced DLCO in COVID-19 survivors without or delayed radiological resolution._ 
_https://aapm.onlinelibrary.wiley.com/doi/10.1002/mp.16915: a deep learning approach to modeling LFT, including DLCO with CT data in large data sets (s8K+ for training) of CT scans, allows for DLO predictions for single lobes; please have a look at Figure 3, where they report correlations between the observed and predicted DLCO - they are not so much better than our best GBM model of DLCO._
_https://pubs.rsna.org/doi/full/10.1148/radiol.221488: they succeeded at predictions of FEV1, FVC, and FEV1:FVC using deep learning (neuronal network) and a large data set of CT images._
_https://pmc.ncbi.nlm.nih.gov/articles/PMC8264499/: a nice review with a short description of algorithms._

@@

### Issue

After adding the literature review, add a summary table and clearly mention this study's research gaps and contributions.

### Response

_Anna and Gerlig, here some my thoughts: As I see our results as a bigger picture: we were limited by the number of patients and by the fact that we worked with processed CT data: scores and values of opacity/high opacity, and human-identified findings - for this limited information, we established quite nice models of DLCO and reduced DLCO < 80%._ 
_There are already some papers on machine learning and lung function._ 
_What looks pretty novel to me: we are among the first groups who used not only the CT information for modeling but also clinical and demographic data._ 
_We also integrate information derived from CT by a software and a human radiologist, which is also a quite novel approach._

@@

### Issue

More details, such as features, are required in the study data.

### Response

Our manuscript is accompanied by a thorough information on patients, procedures, and study variables provided in __Supplementary Methods__. 
Please refer to __Supplementary Table S2__ for a detailed listing of modeling response and explanatory variables with their format and descriptions.

@@

### Issue

The paper lacks details about hyper-parameters for machine learning models. 
For example, what was the C and class weight value for the SVM model?

### Response

Thanks for this point. 
We agree that the information on hyper-parameters in the initial submission was hard to understand for many clinical readers and too specific. 
In the revised manuscript, we provide short descriptions of the hyper-parameters in __Supplementary Methods/Multi-parameter modeling of lung function__. 
These descriptions were also added as footnotes of __Supplementary Table S6__.

@@

### Issue

Have you considered the GridSearchCV for model hyper-parameters or set it manually?

### Response

Thanks for this question. 
The hyper-parameters were found by searching grids of values with the maximum Youden's J statistic for the classification models, and minimum mean absolute error (MAE) for the regression models in 10-repeats 10-fold patient-blocked cross-validation as the selection criteria. 
This tuning procedure was executed by calling `train()` function from _caret_ package [@Kuhn2008], which, together with our open-source package [_caretExtra_](https://github.com/PiotrTymoszuk/caretExtra), belongs to our standard toolbox for explainable machine learning. 
This information is provided in __Supplementary Methods/Multi-parameter modeling of lung function__.

@@

### Issue

Comparison with state-of-the-art studies is missing.

### Response

_Anna and Gerlig: you may consider examples of papers above._

@@

### Issue

Conclusion also not well presented.

### Response

_Anna and Gerlig: I have few thoughts on conclusions:)_ 
_First of all: we demonstrate the feasibility of a machine learning approach combining CT readouts with demographic and clinical information on acute COVID-19 and convalescence at predicting DLCO._ 
_Second: this modeling strategy merges information derived from CT images by a software and a human radiologist._
_Third: while we constructed meaningful models of DLCO, our machine learning models failed to predict FEV1 and FVC. This lets us reason that DLCO but not FEV1 or FVC is the prime LFT readout of post-COVID-19 structural lung damage. By univariable analyses we show that DLCO is tightly associated with CT readouts of severity of lung damage such as CTSS, opacity, or high opacity._

@@

### Issue

The introduction does not sufficiently contextualize how other published multi-parameter or machine learning approaches have succeeded or failed. 
What specific gaps remain? 
A more detailed table is needed to perform the literature review.

### Response

_Anna and Gerlig: please respond. From my quite cursory search of the literature, I've an impression that there are indeed reports with more or less successful trials of prediction of LFT based on CT data - mostly raw images._ 
_In turn, I was not able to find a single modeling papers, where someone tried to combine the demographic, clinical, and rariological information to predict LFT outcomes._ 
_One can say: that the clinic and demography is irrelevant, once you have CT data._ 
_To me it is not, our combination approach let us understand the clinical background and identify some broad risk hactors such as patient's sex and comorbidities._

@@

### Issue

More details about selection and potential biases (e.g., dropouts, missing visits) are needed for the data set.

### Response

We appreciate this point. 
While the CovILD cohort has been already extensively described in our previous papers [@Luger2022; @Sonnweber2022; @Sonnweber2020; @Sahanic2023], we provided in the revised manuscript information on the drop-ou rates at particular time points as compared with the initial collective of n = 145 patients. 
We also references numbers and percentages for the categorical modeling responses (DLCO < 80%, FEV1 < 80%, and FVC < 80%).

@@

### Issue

It remains unclear how each scoring system aligns, differs, or complements the other.

### Response

_Anna and Gerlig: I'd suggest 1 - 2 sentences in Discussion with emphasis that CTSS is a human-derived discretized severity score averaged over the entire lung, and opacity and high opacity are continuous readouts of lesion extent computed by the software. CTSS is expected to be more coarse the opacity or high opacity and cannot accurately capture severe, highly localized cases such as severe damage restricted to only one lobe (it is scored with 5, the same as minimal damage in all lobes). In our data set, CTSS, opacity, and high opacity are strongly inter-correlated._

@@

## Point 15

### Issue

Overemphasis on “satisfactory accuracy” without deeper clinical context.

We apologize for this vague term. 
In the revised manuscript, avoid suggestive phrases on model performance and stick to teh performance metrics and evaluations.

@@

### Issue

The neural network model performed poorly for DLCO.

### Response

In __Review Figure \@ref(fig:fig-dlco-correlations)__ we present correlations between the observed DLCO expressed as percentages of the patient's reference and the out-of-fold predictions of DLCO in participant-blocked 10-repeats 10-fold cross-validation for all four machine learning algorithm. 
To facilitate the comparison, we set ranges of the X and Y axes to the range of observed DLCO values - we applied this transformation to the respective scatter plots in __Figure 2__ as well. 
From this visualization it is that predictions by the neural network algorithm were shrunk to the 75% - 100% range and the neural network algorithm failed to predict cases with very low and very high values of DLCO. 
We can only speculate on the reasons for this behavior, yet, inclusion of more observations with at the lowest and the highest tail of DLCO is expected to improve performance of not only the neural net but also of the remaining models.

@@

### Issue

The SHAP analysis identifies “top 15” predictors. 
However, the manuscript does not address correlations among those predictors or discuss whether certain features might be redundant.

### Response

Thanks for this is a very good point. 
In the initial manuscript, we presented results of exploratory analysis of the modeling data set including the overlap between radiological lung findings, and correlations between opacity, high opacity and CTSS (__Supplementary Figure S3__) - which were also identified as highly influential explanatory factors for prediction of DLCOP < 80% and DLCO (__Figure 3__ and __Supplementary Figure S14__). 
In the revised manuscript, we specifically addressed associations between the most influential explanatory variables with an analysis of correlations graph [@Csardi2006; @Zhang2005] (__Supplementary Figure S15__). 
The graph edges were defined by pairwise correlations between the explanatory factors with Kendall's $\tau \geq$ 0.3 and weighted by $\tau$ values. 
For computation of the correlations, ordinal factors such as presence of GGS of severity of acute COVID-19 were transformed to integers. 
This analysis supports the findings of the initial manuscript version that the CT readouts: CTSS, opacity, high opacity, GGO and reticulations are tightly inter-correlated. 
Another cluster of tightly associated features was formed by readouts of severity of ACUTE COVID-19 such as acute COVID-19 severity, hospital and ICU stay, and anti-infective treatment during acute COVID-19. 
Another community of the influential features was made up by known risk factors of severe COVID-19 course (age, cardiovascular disease, hypercholesterolemia, and endocrine/metabolic disease). 
This leads us to the conclusion that there was indeed some redundancy between the modeling variables and a potential for pruning e.g. by regularization. 
These new results were also briefly discussed.

@@

_Anna and Gerlig: please respond._

## Point 19

### Issue

The paper concedes “model over-fitting” could be an issue. 
However, it lacks any systematic attempt (e.g., a learning-curve analysis or thorough regularization strategy) to demonstrate that over-fitting is minimal or under control.

@@

### Response

Thanks for raising this important issue. 
As suggested, we tacked it by a learning curve analysis [@Viering2023] for the predictions of DLCO < 80% and DLCO by the best performing GBMm models presented in __Supplementary Figure S13__. 
The over-fitting was particularly evident for the predictions of DLCO < 80% as visualized by a slow convergence of curves of accuracy and Cohen's $\kappa$ for training and test subsets of increasing sizes derived from the modeling data and cross-validation. 
By contrast, we can argument that over-fitting of for predictions of DLCO expressed as percentages of the patient's reference was under control. 
We list over-fitting explicitly as a limitation in the revised manuscript and propose regularized algorithms such as XGBoost as a possible remedy. 
We we will certainly consider such algorithms in future studies.

In order to investigate the over-fitting behavior of the models of DLCO < 80%, we resorted to an analysis of the cross-validated model's performance as a function of increasing DLCO percentages. 
As shown in __Supplementary Figure S12__, we found out that the models made uncertain/erroneous predictions - and hence generalized poorly - for observations with DLCO ranging from 70% - 80% of the patient's reference. 
This phenomenon can be explained by the observation that the 80% DLCO cutoff - used in multiple COVID-19 papers [@Zhang2022a; @Sonnweber2020] did not yielded two clearly separated groups of observations in our modeling data set and may not correspond to differences in demographic and clinical background. 
In addition, we believe that expansion observations with DLCO < 80%, either be increasing the cohort size or augmentation of the data set, e.g. by SMOTE [@Chawla2002], may at least partly correct this behavior.

# Review Figures

```{r fig-dlco-correlations, fig.width = figur::convert(rev_figs$dlco_correlations, to = 'in')$w, fig.height = figur::convert(rev_figs$dlco_correlations, to = 'in')$h, fig.cap = 'Correlation of predicted and observed diffusion capacity for carbon monoxide during COVID-19 convalescence'}

rev_figs$dlco_correlations$plot

__Review Figure \@ref(fig:fig-dlco-correlations). Correlation of predicted and observed diffusion capacity for carbon monoxide during COVID-19 convalescence__

_Machine learning models of diffusion capacity for carbon monoxide (DLCO) expressed as percentage of the patient's reference were developed with the random forest, gradient boosted machines (GBM), support vector machines with radial kernel (SVM), and single hidden layer neural network as presented in Figure 2 of the manuscript._ 
_Correlations between the predicted and observed DLCO´values were metered by Spearman's correlation coefficient $\rho$._ 
_The observed DLCO values and out-of-fold DLCO predictions (participant-blocked 10-repeats 10-fold cross-validation [CV]) are visualized with scatter plots. Each point represents a single observation. The blue dashed lines with slope 1 and intercept 0 represent absolutely accurate predictions, general additive model trends with standard errors are visualized as the solid blue lines with gray ribbons. Numbers of complete observations and $\rho$ coefficients are displayed in the plot captions. Ranges of displayed DLCO values were set to the range of observed DLCO._

### 2025-03-09 paper/markdown/manuscript.Rmd
Rebuttal letter
Backbone of the rebuttal letter, figure for the reviewers

Our study has limitations. 
First, the overall patient and observation number was low, in particular for ambulatory COVID-19 convalescents. 
Analogically, the study cohort was enriched in hospitalized individuals with in constitute a minute fraction of COVID-19 patients in the real world setting. 
Second, complete sets of longitudinal CT and LFT measurements at the two-, three-, six- and twelve-month follow-up examinations were available solely for `r covild$ct %>% blast(ID) %>% map_dbl(nrow) %>% map_lgl(~.x == 4) %>% sum` patients. 
Especially the number of observations obtained with ambulatory and moderate COVID-19 convalescents at the six- and twelve-month follow-up were substantially lower as compared with earlier time points. 
The incompleteness of the longitudinal data may have hence compromised performance of the machine learning models in particular for ambulatory COVID-19 cases and at the later time points. 
Third, because of the limited number of participants and observations, we abstained from definition of a test subset of the data used solely for bias-free model evaluation (hold-out strategy). 
Instead, both model selection and evaluation was done with blocked repeated cross-validation, which may have overestimated performance of the models. 
Hence, external validation of our findings in an independent cohort is recommended. 
Fourth, as inferred from the analysis of learning curves, the models of insufficient DLCO suffered for substantial over-fitting. 
While this problem can be partially traced back to an unsharp distinction between sufficient and reduced DLCO with the 80% reference cutoff, a modeling approach employing regularized machine learning algorithm like XGBoost or regularized neural networks may further improve quality of predictions. 
Furthermore, most of the highly influential explanatory variables for predictions of DLCO and reduced DLCO, and in particular the CT readouts of lung damage were strongly inter-correlated, which raises questions about redundancy of explanatory variables. 
Finally, the analyzed cohort was recruited in the initial phase of the pandemic and consisted of individuals infected with the wild-type variant of the SARS-CoV-2 virus. 
For this reason, it is not completely clear, how our findings translate to the recent variants of the pathogen and how the pulmonary recovery is affected by anti-SARS-CoV-2 immunity, improved treatment and care. 
However, it is feasible, that the CT severity readouts, human-determined CTSS as well as AI-determined opacity and high opacity, are equally applicable in the post-pandemic setting as standalone markers of functional lung impairment during recovery from COVID-19 and other respiratory infections.

@@

__Figure \@ref(fig:fig-ml-performance). Evaluation of performance of machine learning models of diffusion capacity for CO during COVID-19 convalescence.__

@@

_(B) Four machine learning regression models of diffusion capacity for carbon monoxide (percentage of reference values, total observations: n = `r nobs(reg_models$models$DLCO_percent[[1]])`) employing time after COVID-19 diagnosis, computed tomography readouts, demographic and clinical explanatory variables were trained. Their performance was evaluated in th entire data set and 10-repeats 10-fold cross-validation with $R^2$ as a measure of explained variation, mean absolute error, and $\rho$ Spearman's coefficient of correlation between the predicted and observed values. Bubble plot: numeric performance measures of the model (open circles: the entire data set, filled circles: cross-validation); point sizes and point labels represent values of $\rho$ correlation coefficient, the dashed line visualizes $R^2$ value expected for a meaningless model. Scatter plots: observed and predicted values of diffusion capacity for carbon monoxide in cross-validation folds; the blue dashed lines with slope 1 and intercept 0 represent absolutely accurate predictions, general additive model trends with standard errors are visualized as the solid blue lines with gray ribbons. Numbers of complete observations and Spearman's $\rho$ coefficients of correlation between the predicted and observed values are displayed in the plot captions._

>>>>

Our study has limitations. 
First, the overall patient and observation number was low, in particular for ambulatory COVID-19 convalescents. 
Analogically, the study cohort was enriched in hospitalized individuals with in constitute a minute fraction of COVID-19 patients in the real world setting. 
Second, complete sets of longitudinal CT and LFT measurements at the two-, three-, six- and twelve-month follow-up examinations were available solely for `r covild$ct %>% blast(ID) %>% map_dbl(nrow) %>% map_lgl(~.x == 4) %>% sum` patients. 
Especially the number of observations obtained with ambulatory and moderate COVID-19 convalescents at the six- and twelve-month follow-up were substantially lower as compared with earlier time points. 
The incompleteness of the longitudinal data may have hence compromised performance of the machine learning models in particular for ambulatory COVID-19 cases and at the later time points. 
Third, because of the limited number of participants and observations, we abstained from definition of a test subset of the data used solely for bias-free model evaluation (hold-out strategy). 
Instead, both model selection and evaluation was done with blocked repeated cross-validation, which may have overestimated performance of the models. 
Hence, external validation of our findings in an independent cohort is recommended. 
Fourth, as inferred from the analysis of learning curves, the models of insufficient DLCO suffered for substantial over-fitting. 
While this problem can be partially traced back to an unsharp distinction between sufficient and reduced DLCO with the 80% patient's reference cutoff, a modeling approach employing regularized machine learning algorithm like XGBoost or regularized neural networks may further improve quality of predictions. 
Fifth, most of the highly influential explanatory variables for predictions of DLCO and reduced DLCO, and in particular the CT readouts of lung damage were strongly inter-correlated, which raises questions about redundancy of explanatory variables. 
Furthermore, CT-related explanatory variables were already processed and available in form of software- and human-derived severity metrics and findings without any spatial information. 
Inclusion of raw CT image information in the machine learning models would likely enhance their accuracy, as demonstrated by literature reports. 
Finally, the analyzed cohort was recruited in the initial phase of the pandemic and consisted of individuals infected with the wild-type variant of the SARS-CoV-2 virus. 
For this reason, it is not completely clear, how our findings translate to the recent variants of the pathogen and how the pulmonary recovery is affected by anti-SARS-CoV-2 immunity, improved treatment and care. 
However, it is feasible, that the CT severity readouts, human-determined CTSS as well as AI-determined opacity and high opacity, are equally applicable in the post-pandemic setting as standalone markers of functional lung impairment during recovery from COVID-19 and other respiratory infections.

@@

__Figure \@ref(fig:fig-ml-performance). Evaluation of performance of machine learning models of diffusion capacity for carbomn monoxide during COVID-19 convalescence.__

@@

_(B) Four machine learning regression models of diffusion capacity for carbon monoxide (percentage of reference values, total observations: n = `r nobs(reg_models$models$DLCO_percent[[1]])`) employing time after COVID-19 diagnosis, computed tomography readouts, demographic and clinical explanatory variables were trained. Their performance was evaluated in th entire data set and 10-repeats 10-fold cross-validation with $R^2$ as a measure of explained variation, mean absolute error, and $\rho$ Spearman's coefficient of correlation between the predicted and observed values. Bubble plot: numeric performance measures of the model (open circles: the entire data set, filled circles: cross-validation); point sizes and point labels represent values of $\rho$ correlation coefficient, the dashed line visualizes $R^2$ value expected for a meaningless model. Scatter plots: observed and predicted values of diffusion capacity for carbon monoxide in cross-validation folds; the blue dashed lines with slope 1 and intercept 0 represent absolutely accurate predictions, general additive model trends with standard errors are visualized as the solid blue lines with gray ribbons. Numbers of complete observations and Spearman's $\rho$ coefficients of correlation between the predicted and observed values are displayed in the plot captions. Ranges of the displayed DLCO values were set to the range of observed DLCO._

### 2025-03-09 paper/markdown/supplementary_material.Rmd
Rebuttal letter
Backbone of the rebuttal letter, figure for the reviewers

Hyper-parameters that control the modeling algorithm's behavior were found by maximizing the Youden's J statistic 
($J = Sensitivity + Specificity - 1$, classification models of binary LFT outcomes) or by minimizing mean absolute error (MAE, regression models of numeric LFT outcomes) in 10-repeats 10-fold cross-validation, in a process called tuning. 
The tunable hyper-parameters were:

@@

To account for the participant matching of the observations in the cross-validated tuning of hyper-parameters, a blocked cross-validation design was applied to keep all observations obtained from a particular participant either in the training or in the test portion of the cross-validation split. 
Construction of such 'participant-wise' blocked cross-validation folds was done with an in-house-developed wrapper around `createMultiFolds()` function (package _caret_). 
For tuning and training of the machine learning models, the `train()` wrapper from the _caret_ package was employed [@Kuhn2008]. 
The optimal values of the tuning parameters are listed in __Supplementary Table S\@ref(tab:tab-tuning)__.

@@

The most influential explanatory factors for predictions of DLCO (algorithms: random forest, GBM, neuronal network, and SVM radial) and DLCO < 80% of reference (algorithms: random forest, GBM, SVM radial) were identified as top 15 variables with the largest mean absolute SHAP importance values for each of the modeling algorithms. 
Associations between these highly influential variables were assessed with a soft-threshold weighted graph of correlations, a method widely used in omics and system biology [@Csardi2006; @Zhang2005]. 
For construction of the correlation graph, ordered categorical variables (i.e. factors in R) were converted to integers. 
The graph edges were defined by pairwise correlations between the variables with Kendall's $\tau \geq 0.3$. 
The edge weights corresponded to values of the $\tau$ correlation coefficients. 
The graph was constructed with `as_iGraph()` function; isolated vertices, i.e. variables without any correlations with $\tau \geq$ 0.3 were removed from the graph with `prune_degree()` (both functions from [_graphExtra_](https://github.com/PiotrTymoszuk/graphExtra)). 
The graph was visualized with Fruchterman-Reingold algorithm (method `plot()`, package [_graphExtra_](https://github.com/PiotrTymoszuk/graphExtra)).

>>>>

Hyper-parameters that control the modeling algorithm's behavior were found by searching grids of hyper-parameter values with maximizing the Youden's J statistic 
($J = Sensitivity + Specificity - 1$, classification models of binary LFT outcomes) or by minimizing mean absolute error (MAE, regression models of numeric LFT outcomes) in 10-repeats 10-fold cross-validation, in a process called tuning. 
The tunable hyper-parameters were:

@@

To account for the participant matching of the observations in the cross-validated tuning of hyper-parameters, a blocked cross-validation design was applied to keep all observations obtained from a particular participant either in the training or in the test portion of the cross-validation split. 
Construction of such 'participant-wise' blocked cross-validation folds was done with an in-house-developed wrapper around `createMultiFolds()` function (package _caret_). 
For tuning and training of the machine learning models, the `train()` wrapper from the _caret_ package was employed; the tuning/training setting such as participant-blocked indexes for cross-validation folds and Youden's J cost function was specified by via a `trainControl()` object provided to the `train()` function [@Kuhn2008]. 
The optimal values of the tuning parameters are listed in __Supplementary Table S\@ref(tab:tab-tuning)__.

@@

The most influential explanatory factors for predictions of DLCO (algorithms: random forest, GBM, neuronal network, and SVM radial) and DLCO < 80% of reference (algorithms: random forest, GBM, SVM radial) were identified as top 15 variables with the largest mean absolute SHAP importance values for each of the modeling algorithms. 
Associations between these highly influential variables were assessed with a soft-threshold weighted graph of correlations, a method widely used in omics and system biology [@Csardi2006; @Zhang2005]. 
For construction of the correlation graph, ordered categorical variables (i.e. factors in R) were converted to integers. 
The graph edges were defined by pairwise correlations between the variables with tie-adjusted Kendall's $\tau \geq 0.3$. 
The edge weights corresponded to values of the $\tau$ correlation coefficients. 
The graph was constructed with `as_iGraph()` function, the correlation matrix was computed with `cor()` function from _stats_ package passed to`as_iGraph()`. 
Isolated vertices, i.e. variables without any correlations with $\tau \geq$ 0.3 were removed from the graph with `prune_degree()` (both functions from [_graphExtra_](https://github.com/PiotrTymoszuk/graphExtra)). 
The graph was visualized with Fruchterman-Reingold algorithm (method `plot()`, package [_graphExtra_](https://github.com/PiotrTymoszuk/graphExtra)).
